%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\todo{\paragraph{Overall TODOs.}\begin{itemize}
    \item Use $\mathbf{p}$ to denote projections everywhere (also double-check figures, plot axes, legends, etc.).
    \item Index all objects using subscripts. Report all results in radians. Use sentence case. Use American English.
\end{itemize}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\todo{\paragraph{STILL TO DISCUSS.}\begin{itemize}

    \item \mdeff{Laurène, how much do you like this double spacing? ;)} \lau{We can totally switch back to single spacing, it was just easier for me to go through the document on my iPad with double spacing ^^}

    \item Orientations: Use $q$ or $\boldsymbol\theta$ for the orientation, and $\mathbf{R}$ for rotation. Settle after writing \secref{method:orientation-representation}.

    \item Distance functions: orientations $\SO(3)$ geodesic $d_o$, projections Euclidean $d_{pe}$, projections learned $d_{pl}$. \lau{Let's settle on that.}

    \item Consistency: convergence curves must all have the same x-axis (time, step, or epoch). \mdeff{I think epoch would be good.}

    \item $\SO(3)$ half coverage (it is $S^2$ half coverage). \mdeff{Agreed.}

\end{itemize}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\todo{\paragraph{TO KEEP IN MIND.}\begin{itemize}
    \item phrases to keep all along: distance estimation (verb: estimate distances), distance learning (verb: learn distance), orientation recovery (verb: recover orientations)
    \item Typography: \mdeff{footnotes after periods, em dashes, Oxford comma, commas after i.e.\ and e.g., (i) and (ii). Again no strong feeling, most important is consistency.}
    \item Give meaningful and consistent names to figures. To avoid confusion, label = figure name.
    \item Bold face for vectors and matrices. \mdeff{That's quite signal processing. Is the cryo-EM community using this convention?} \lau{They do as well.} \mdeff{Ok then we do that.}
\end{itemize}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
